The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-08 paper/ms.tex
Move section 3 around, add couple sentences

\section{Coordinate System Offsets I. Measurement Errors} \label{sec:mes_err}
We consider the first potential source of coordinate system offsets which
would generate the action errors described in Section~\ref{sec:ref_frame}:
uncertainties in measurements of the position and velocity of the Sun relative
to the Galactic center. Converting from heliocentric to Galactocentric
coordinates relies on these measurements. Therefore, errors in their values
will induce a systematic offset in the Galactocentric phase-space position of
any observed star.

\subsection{Solar Height}
Third, one must define the Sun's vertical distance from the Galactic midplane,
which can be determined by identifying where the stellar density and
velocities reach a maximum (effectively the median height of all disk stars).
The Solar height is usually taken to be $\sim 25\,\pc$
\citep{2001ApJ...553..184C}, with a more recent measurement from \textit{Gaia}
DR2 placing it at $20.8 \pm 0.3\,\pc$ \citep{2019MNRAS.482.1417B}. Another
strategy is to use the cold gas or H~\textsc{ii} regions in the disk to define
the Galactic midplane, leading to slightly different values (by $\sim 5\,\pc$)
for the Sun's relative height \citep[e.g.][]{2019ApJ...871..145A}. A pre-{\em
Gaia} review of these measurements is given by \citet{2016ARAA..54..529B}.

\section{Coordinate System Offsets II. Azimuthal Midplane Variations in
Simulations}
\label{sec:local_fire}

We now consider a second source of systematic offsets in the Galactocentric
coordinate system: intrinsic variations of the midplane across the disk. In
this work we specifically consider azimuthal variations in the midplane as
defined by the stellar mass density. We use two sets of simulations of Milky
Way-mass galaxies to estimate the size of this effect.

@@

>>>>

\section{Coordinate System Offsets I. Azimuthal Midplane Variations in
Simulations}
\label{sec:local_fire}

We first consider one source systematic offsets in the Galactocentric
coordinate system: intrinsic variations of the midplane across the disk. In
this work we specifically consider azimuthal variations in the midplane as
defined by the stellar mass density. We use two sets of simulations of Milky
Way-mass galaxies to estimate the size of this effect.

@@

\section{Coordinate System Offsets II. Measurement Errors} \label{sec:mes_err}
We consider the second potential source of coordinate system offsets which
would generate the action errors described in Section~\ref{sec:ref_frame}:
uncertainties in measurements of the position and velocity of the Sun relative
to the Galactic center. Converting from heliocentric to Galactocentric
coordinates relies on these measurements. Therefore, errors in their values
will induce a systematic offset in the Galactocentric phase-space position of
any observed star.

In the epicyclic approximation (Section~\ref{ssec:epi_action}), the $0.3\%$
error in $R_0$ induces a $5.4\%$ and $5.9\%$ error in the thin-disk and
thick-disk orbits, respectively. For $J_{\phi}$, the error is $0.3\%$ for both
orbits.

\subsection{Solar Height}
Third, one must define the Sun's vertical distance from the Galactic midplane, $z_{\odot}$.
It can be determined by identifying where the stellar density and
velocities reach a maximum (effectively the median height of all disk stars).
The Solar height is usually taken to be $\sim 25\,\pc$
\citep{2001ApJ...553..184C}, with a more recent measurement from \textit{Gaia}
DR2 placing it at $20.8 \pm 0.3\,\pc$ \citep{2019MNRAS.482.1417B}. Another
strategy is to use the cold gas or H~\textsc{ii} regions in the disk to define
the Galactic midplane, leading to slightly different values (by $\sim 5\,\pc$)
for the Sun's relative height \citep[e.g.][]{2019ApJ...871..145A}. A pre-{\em
Gaia} review of these measurements is given by \citet{2016ARAA..54..529B}.

Under the epicyclic approximation, the highest precision measurement of
$z_{\odot}$ of $1.4\%$ from \citet{2019MNRAS.482.1417B} induces a $0.5\%$ and
$0.04\%$ error in $J_z$ for the thick-disk and thin-disk orbits, respectively.
The discrepancy between the stellar and gas midplanes of $\sim5\,\pc$ induces
an $8.3\%$ and $1.2\%$ error in $J_z$ for the two orbits.
